Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2017-09-08 stp/paper_aaai/main.tex
Small fixes to charts and appendices

\newcommand{\minizinc}{\textsc{MiniZinc}}
\newcommand{\chuffed}{\textsc{Chuffed}}
\newcommand{\relonto}{\textsc{Rel2Onto}}
\newcommand{\karma}{\textsc{Karma}}
\newcommand{\serene}{\textsc{Serene}}
\newcommand{\serenepats}{\textsc{SerenePats}}

@@

\begin{figure}[!htb]
\begin{minipage}[b]{.5\linewidth}
\centering
\hspace*{-15pt}
\begin{tikzpicture}[baseline,scale=0.43]
\begin{axis}[
		    xlabel={\emph{known semantic models}},
		    ylabel={},
		    xmin=1, xmax=28,
		    ymin=0.2, ymax=0.9,
		    xtick={1,5,10,15,20,25,28},
		    ytick={0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1},
		    legend pos=south east,
		    ymajorgrids=true,
		    grid style=dashed,
		    style = {font=\huge}
		]

@@

		\end{axis}
\end{tikzpicture}
\subcaption{Precision (museum)}\label{fig:museumprec}
\end{minipage}%
\begin{minipage}[b]{.5\linewidth}
\centering
\begin{tikzpicture}[baseline,scale=0.43]
		\begin{axis}[
		    xlabel={\emph{known semantic models}},
		    %ylabel={recall},
		    xmin=1, xmax=28,
		    ymin=0.2, ymax=0.9,
		    xtick={1,5,10,15,20,25,28},
		    ytick={0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1},
		    ymajorgrids=true,
		    grid style=dashed,
		    		    style = {font=\huge},
		    legend style={at={(0.5,1.1)},anchor=south, legend columns=-1}
		]

@@

\begin{axis}[
  axis y line*=left,
  ymin=0.5, ymax=1,
  xlabel=Solution Number,
  ylabel=performance,
  		    		    style = {font=\huge}
]
\addplot[smooth,mark=x,red]
  coordinates{
    (0,0.776507549540743)(1,0.71093042754513)(2,0.822783653218436)(3,0.845760233918129)(4,0.879310344827586)(5,0.88695652173913)(6,0.885964912280702)(7,0.870689655172414)(8,0.878260869565217)(9,0.87719298245614)

}; \label{plot_one}
\addplot[smooth,mark=*,green]
  coordinates{
    (0,0.773180507486795)(1,0.677202255831871)(2,0.805899400726987)(3,0.838122605363985)(4,0.879310344827586)(5,0.879310344827586)(6,0.870689655172414)(7,0.870689655172414)(8,0.870689655172414)(9,0.862068965517241)
}; \label{plot_two}
\end{axis}

\begin{axis}[
  axis y line*=right,
  axis x line=none,
  ymin=0, ymax=15,
  legend pos=south east,
  ylabel=time (s),
  		    		    style = {font=\huge}
]
\addlegendimage{/pgfplots/refstyle=plot_one}\addlegendentry{precision}
\addlegendimage{/pgfplots/refstyle=plot_two}\addlegendentry{recall}
\addplot[smooth,mark=square,blue]
  coordinates{
    (0,0.894338290115883)(1,2.39426428574782)(2,6.89703391393025)(3,10.3563708686829)(4,9.87668780326843)(5,9.92719115257263)(6,10.4045292949677)(7,14.3818371582031)(8,14.4026180458069)(9,14.8023208427429)
}; \addlegendentry{time}
\end{axis}
\end{tikzpicture}
\caption{Performance of \serene{} for leave-one-out strategy on the museum 
domain.}\label{fig:loo}
\vspace{-3mm}
\end{figure}

@@

\begin{table}[h]
	\centering
	\caption{Feature extractors that produce a scalar value}
	\begin{tabular}{p{3cm}p{4.5cm}}
	Feature name & Description \\ \hline
	num-unique-vals & A simple count of unique entries of a column\\
	\rowcolor{Gray}
	prop-unique-vals & The proportion of unique entries of a column. \\
	\rowcolor{Gray}
	prop-missing-vals & The proportion of all missing/empty entries from all entries in a column.\\
	ratio-alpha-chars & The average of the proportion of alphabetic characters from each entry.\\
	\rowcolor{Gray}
	prop-numerical-chars & The average of the proportion of numeric characters from each entry.\\
	prop-whitespace-chars    & The average of the proportion of whitespace characters from each entry.\\
	\rowcolor{Gray}
	prop-entries-with-at-sign& The proportion of entries with an '@' sign. \\
	prop-entries-with-hyphen & The proportion of entries with a '-'. \\
	\rowcolor{Gray}
	prop-range-format        & The proportion of entries which follow some \\ numerical range format &  ([0-9]+)-([0-9]+) \\
	\rowcolor{Gray}
	is-discrete              & A binary indicator if the column entries are discrete. \\
	entropy-for-discrete-values & The entropy of the entries of a column.\\
	\rowcolor{Gray}	
	shannon-entropy          & Shannon's entropy for the vocabulary specified in the description of the feature 'char-dist-features'\\
	\end{tabular}
\end{table}

@@

prop-instances-per-class-in-knearestneighbours         & This finds the k columns from the training set with most similar names.
It then produces a vector of class proportions from these k neighbours.
Parameters:
"num-neighbours": The number of neighbours to find (k).\\
	\rowcolor{Gray}
mean-character-cosine-similarity-from-class-examples   & For some test instance t, this computes the character distribution 
from this instance's entries.  It then produces a vector of the average
cosine similarity of t with training instances of each class.\\
min-editdistance-from-class-examples                   & For some test instance t, this produces a vector of the minimum column name
edit distance between t and all training instances of each class.
Parameters:
"cache-size": Size of cache for storing edit distances of words 
"max-comparisons-per-class": Max number of training instances to compare
against for each class.\\

	\rowcolor{Gray}
min-wordnet-jcn-distance-from-class-examples            & For some test instance t, this produces a vector of the minimum column name
JCN WS4J distance between t and all training instances of each class.
Parameters:
"cache-size": Size of cache for storing wordnet distances of words 
"max-comparisons-per-class": Max number of training instances to compare
against for each class.\\

min-wordnet-lin-distance-from-class-examples            & For some test instance t, this produces a vector of the minimum column name
LIN WS4J distance between t and all training instances of each class.
Parameters:
"cache-size": Size of cache for storing wordnet distances of words 
"max-comparisons-per-class": Max number of training instances to compare
against for each class.\\

@@

% The solver will use these strategies in order:
% 1) First try using the cheapest matches matches, until a match is found
% 2) If there are patterns, use a specific search called "cheap_edges_fill_pattern". (Implemented in Chuffed only)
%    It will start adding edges in increasing order of cost, while trying to fill patterns that are "worth" filling.
%    E.g. We already set es[x] = true for x in {e1,e2,e3}; if adding ws[e5] = 4 and ws[e7] = 6, but
%    {e1,e2,e3,e7} form a pattern p of patterns_w[p] = 3, then ws[e7] - patterns_w[p] <  ws[e5], so e7 is selected first
%    If there are no patterns, this strategy is ignored.
% 3) Try to eliminate edges by decreasing cost: it will eliminate the more expensive edges first, until
%    the strictly necesary cheap edges are added by the propagators. This is used only when there are no 
%    patterns, otherwise (2) already selects the edges.

>>>>

\newcommand{\minizinc}{\textsc{MiniZinc}}
\newcommand{\chuffed}{\textsc{Chuffed}}
\newcommand{\relonto}{\textsc{Rel2Onto}}
\newcommand{\karma}{\textsc{Karma}}
\newcommand{\serene}{\textsc{•}sc{Serene}}
\newcommand{\serenepats}{\textsc{SerenePats}}

@@

\begin{figure}[!htb]
\begin{minipage}[b]{.5\linewidth}
\centering
\hspace*{-15pt}
\begin{tikzpicture}[baseline,scale=0.43]
\begin{axis}[
		    xlabel={\emph{known semantic models}},
		    ylabel={},
		    xmin=1, xmax=28,
		    ymin=0.3, ymax=0.9,
		    xtick={1,5,10,15,20,25,28},
		    ytick={0.3,0.4,0.5,0.6,0.7,0.8,0.9,1},
		    legend pos=south east,
		    ymajorgrids=true,
		    grid style=dashed,
		    style = {font=\huge}
		]

@@

		\end{axis}
\end{tikzpicture}
\subcaption{Precision (museum)}\label{fig:museumprec}
\end{minipage}%
\begin{minipage}[b]{.5\linewidth}
\centering
\begin{tikzpicture}[baseline,scale=0.43]
		\begin{axis}[
		    xlabel={\emph{known semantic models}},
		    %ylabel={recall},
		    xmin=1, xmax=28,
		    ymin=0.3, ymax=0.9,
		    xtick={1,5,10,15,20,25,28},
		    ytick={0.3,0.4,0.5,0.6,0.7,0.8,0.9,1},
		    ymajorgrids=true,
		    grid style=dashed,
		    		    style = {font=\huge},
		    legend style={at={(0.5,1.1)},anchor=south, legend columns=-1}
		]

@@

\begin{axis}[
  axis y line*=left,
  ymin=0.6, ymax=1,
  xmin=1, xmax=10,
  xlabel=Solution Number,
  ylabel=performance,
  		    		    style = {font=\huge}
]
\addplot[smooth,mark=x,red]
  coordinates{
    (1,0.776507549540743)(2,0.71093042754513)(3,0.822783653218436)(4,0.845760233918129)(5,0.879310344827586)(6,0.88695652173913)(7,0.885964912280702)(8,0.870689655172414)(9,0.878260869565217)(10,0.87719298245614)

}; \label{plot_one}
\addplot[smooth,mark=*,green]
  coordinates{
    (1,0.773180507486795)(2,0.677202255831871)(3,0.805899400726987)(4,0.838122605363985)(5,0.879310344827586)(6,0.879310344827586)(7,0.870689655172414)(8,0.870689655172414)(9,0.870689655172414)(10,0.862068965517241)
}; \label{plot_two}
\end{axis}

\begin{axis}[
  axis y line*=right,
  axis x line=none,
  ymin=0, ymax=15,
  xmin=1, xmax=10,
  legend pos=south east,
  ylabel=time (s),
  		    		    style = {font=\huge}
]
\addlegendimage{/pgfplots/refstyle=plot_one}\addlegendentry{precision}
\addlegendimage{/pgfplots/refstyle=plot_two}\addlegendentry{recall}
\addplot[smooth,mark=square,blue]
  coordinates{
    (1,0.894338290115883)(2,2.39426428574782)(3,6.89703391393025)(4,10.3563708686829)(5,9.87668780326843)(6,9.92719115257263)(7,10.4045292949677)(8,14.3818371582031)(9,14.4026180458069)(10,14.8023208427429)
}; \addlegendentry{time}
\end{axis}
\end{tikzpicture}
\caption{Performance of \serene{} for leave-one-out strategy on the museum 
domain.}\label{fig:loo}
\vspace{-3mm}
\end{figure}

@@

\begin{table}[h]
	\centering
	\caption{Feature extractors that produce a scalar value}
	\begin{tabular}{p{3cm}p{4.5cm}}
	Feature name & Description \\ \hline
	num-unique-vals & A simple count of unique entries of a column\\
	\rowcolor{Gray}
	prop-unique-vals & The proportion of unique entries of a column. \\
	\rowcolor{Gray}
	prop-missing-vals & The proportion of all missing/empty entries from all entries in a column.\\
	ratio-alpha-chars & The average of the proportion of alphabetic characters from each entry.\\
	\rowcolor{Gray}
	prop-numerical-chars & The average of the proportion of numeric characters from each entry.\\
	prop-whitespace-chars    & The average of the proportion of whitespace characters from each entry.\\
	\rowcolor{Gray}
	prop-entries-with-at-sign& The proportion of entries with an '@' sign. \\
	prop-entries-with-hyphen & The proportion of entries with a '-'. \\
	\rowcolor{Gray}
	prop-range-format numerical range format  & The proportion of entries which follow some ([0-9]+)-([0-9]+)\\

	is-discrete              & A binary indicator if the column entries are discrete. \\
	\rowcolor{Gray}
	entropy-for-discrete-values & The entropy of the entries of a column.\\
	shannon-entropy          & Shannon's entropy for the vocabulary specified in the description of the feature 'char-dist-features'\\
	\end{tabular}
\end{table}

@@

prop-instances-per-class-in-knearestneighbours         & This finds the k columns from the training set with most similar names.
It then produces a vector of class proportions from these k neighbours.
Parameters:
"num-neighbours": The number of neighbours to find (k).\\
	\rowcolor{Gray}
mean-character-cosine-similarity-from-class-examples   & For some test instance t, this computes the character distribution 
from this instance's entries.  It then produces a vector of the average
cosine similarity of t with training instances of each class.\\
min-editdistance-from-class-examples                   & For some test instance t, this produces a vector of the minimum column name
edit distance between t and all training instances of each class.
Parameters:
"cache-size": Size of cache for storing edit distances of words; 
"max-comparisons-per-class": Max number of training instances to compare
against for each class.\\

	\rowcolor{Gray}
min-wordnet-jcn-distance-from-class-examples            & For some test instance t, this produces a vector of the minimum column name
JCN WS4J distance between t and all training instances of each class.
Parameters:
"cache-size": Size of cache for storing wordnet distances of words;
"max-comparisons-per-class": Max number of training instances to compare
against for each class.\\

min-wordnet-lin-distance-from-class-examples            & For some test instance t, this produces a vector of the minimum column name
LIN WS4J distance between t and all training instances of each class.
Parameters:
"cache-size": Size of cache for storing wordnet distances of words; 
"max-comparisons-per-class": Max number of training instances to compare
against for each class.\\

@@

% The solver will use these strategies in order:
% 1) First try using the cheapest matches, until a match is found
% 2) If there are patterns, use a specific search called "cheap_edges_fill_pattern". (Implemented in Chuffed only)
%    It will start adding edges in increasing order of cost, while trying to fill patterns that are "worth" filling.
%    E.g. We already set es[x] = true for x in {e1,e2,e3}; if adding ws[e5] = 4 and ws[e7] = 6, but
%    {e1,e2,e3,e7} form a pattern p of patterns_w[p] = 3, then ws[e7] - patterns_w[p] <  ws[e5], so e7 is selected first
%    If there are no patterns, this strategy is ignored.
% 3) Try to eliminate edges by decreasing cost: it will eliminate the more expensive edges first, until
%    the strictly necesary cheap edges are added by the propagators. This is used only when there are no 
%    patterns, otherwise (2) already selects the edges.
